--- 
title: "Streamline Model Development - Demo"
author: "Lizzy Huang"
date: "`r Sys.Date()`"
site: bookdown::bookdown_site
output: bookdown::gitbook
documentclass: book
bibliography: [book.bib, packages.bib]
biblio-style: apalike
link-citations: yes
description: "This is a minimal example of using the bookdown package to write a book. The output format for this example is bookdown::gitbook."
---

```{r load-libraries-n-data, echo = F, warning=F, message=F}
## load libraries
library(dplyr)
library(ggplot2)
library(glmnet)
source("C:/demo/package.R")

## load data
game = get(load("C:/demo/game.Rdata"))
```

```{r include=FALSE}
# automatically create a bib database for R packages
knitr::write_bib(c(
  .packages(), 'bookdown', 'knitr', 'rmarkdown'
), 'packages.bib')
```


# Introduction

This is a demo about how to streamline model development process with synchronized documentation using **R Markdown**. Here we only show a sample procedure where we have a general logistic regression model that will apply to 2 different subsets of the data, corresponding to 2 different "products". The ability of **bookdown** using separate `.Rmd` files for different sections of the documentation provides more flexibility for collaboration.

