# Data

```{r load-data, echo = FALSE}
## load data
game = get(load("game.Rdata"))
```


Assuming that part of the data extraction part has been completed, we start directly with the data analysis part.

In this example, we use the data sets from the [**Kaggle European Soccer Database**](https://www.kaggle.com/hugomathien/soccer) to estimate the likelihood of winning, losing and getting a draw of soccer games in the Premier League based on several related variables. There are in total 608 games in 8 seasons, with 304 home games and 304 away games. The data set has been pre-processed for this demo.

## Variables Summary

In this model, we use the following variables extracted from the **match events**


Variables | Definitions |
--------------------------------------------|----------------------------------------------------|
`match id` | unique ID for every match |
`team_long_name` | the name of the team |
`season`   | match season, from 2008/2009 to 2015/2016 |
`team_goal` | the number of goals the team scored in the match |
`opponent_goal` | the number of goals the opponent team scored in the match|
`game_type` | identify whether it's a home game or an away game |
`result` | match results, either win, loss, or draw |
`team_foul`, `opponent foul` | the number of fouls the team / opponent team committed in the match |
`team_rcard`, `team_ycard`, `opponent_rcard`, `opponent_ycard` | the numbers of red/yellow cards that the team/opponent team received |
`team_cross`, `opponent_cross` | the number of crosses of the team / opponent team made |
`team_corner`, `opponent_corner` | the number of corners the team / opponent team received |
`team_shotoff`, `opponent_shotoff` | the number of shot-offs the team / opponent team made |
`team_shoton`, `opponent_shoton` | the number of shot-ons the team / opponent team made |
`team_pos`, `opponent_pos` | the percentage of possession the team / opponent team had. The two adds up to be 100 |


## Training Data and Testing Data


```{r ignore-missing, echo = FALSE}
missing = sum(!complete.cases(game))
game_clean = game[complete.cases(game), ]

train.seasons = c("2008/2009", "2009/2010", "2010/2011", "2011/2012", "2012/2013", "2013/2014", "2014/2015")

training.df = game_clean[game_clean$season %in% train.seasons, ]
test.df = game_clean[!(game_clean$season %in% train.seasons), ]

training.num = nrow(training.df)
test.num = nrow(test.df)
```

We select seasons 2008/2009 - 2014/2015 as the training data, and the last season 2015/2016 as the testing data. We exclude observations which have missing values in one or more columns. This leaves us `r training.num` games in the training set and `r test.num` games in the testing set.

### Input Variable Analysis

Here, we summarise the distributions of some of the input variables from the training data set, say, the distribution of `team_shoton` based on the results.

```{r plot-team_shoton, echo = FALSE, message = FALSE, fig.height = 4}
ggplot(data = training.df) + 
  geom_histogram(aes(x = team_shoton)) + facet_wrap(~result) + xlab("Number of shot-ons") + 
  ggtitle("Distribution of Shot-ons")
```

### Output Variable - `result`

We show the counts of the 3 results: draw, loss, win. 

```{r echo = FALSE}
ggplot(data = training.df) + geom_bar(aes(x = result)) + 
  ggtitle("Numbers of game results")
```



